\indent
\par
Team BirdFeedr is a small group of student software developers. Our members are Josh Gillham, Wei Huang, Thomas Macari, Miguel Roman, Di Tran, and Nate Witt.
\smallskip
\par
Our mission as Team BirdFeedr is to inspire people to reach their computer science dreams by providing tools that help them overcome the barriers of programming.
\smallskip
\par
Team BirdFeedr chose to develop an extension for the BlueJ IDE for their CS4260 class.
We decided on our tools and to follow Agile methodologies that we previously learned in CS 4250 to tackle the contents of the extension.
We held several team building events, communicated through email, voice chat, live person, and created group policies to effectively establish communication between members of the group.
\smallskip
\par
We then explored BlueJ’s API by creating exploration projects.
After the exploration projects, we conducted a survey and found that students had a difficult time understanding the syntax and nature of computer languages and programming. From this information, we decided on a BlueJ extension that would assist our users in understanding how to program.
\smallskip
\par
The name of our extension is BlueJ TA. BlueJ TA's current features include: Being able to work on exercises using the BlueJ IDE, loading exercises from a local folder, and giving quick feedback on the correctness of the exercises. 
\smallskip
\par
Our product is by no means complete, but it contains a complete framework that future developers can build on.
Our repository contains all the source files, as well as a build file so developers can immediately start working.
Bundled with our product are some sample exercises so users can practice right away.
\smallskip
\par
Overall, our time in Software Engineering Practices has proven fruitful, and this portfolio demonstrates that a team of 6 senior students, when working together, can produce a product that is not only demonstrable immediately, but also has enough forethought that when it will be passed on, it can be further developed into the product it was envisioned to be.

